\bf Calendar-based graphics for visualizing people's daily schedules

### 2018-10-22 main.Rmd
di finished

As a data restructuring tool, the interactivity of calendar-based display can be easily enabled, as long as the interactive graphic system remains true to the spirit of the grammar of graphics, for example **plotly** [@plotly] in R. As a standalone display, interactive tooltip can be added to show the actual values of a data point when mousing over it in the calendar layout, for example the hourly count with the time of day. It is difficult to sense the values in static display, but the tooltip makes it possible. Options in function `frame_calendar` can be ported to a form of selection buttons or text input. The display will update on the fly accordingly via clicking or inputing, as desired.

Linking calendar displays to other types of charts is of great value to visually explore the interactions with many factors. It most naturally serves as a toolbox of date selection. By selecting and brushing the glyphs in the calendar, it subsequently highlights the elements of corresponding dates in other time-based plots, or vice versa. For example, it would be interesting to learn if very hot/cold days and heavy rain affect the number of people walking in downtown Melbourne, especially outdoor areas. Melbourne's daily temperatures and precipitations can be acquired, and plotted against the dates. The linking between weather data and calendar display is achieved using the common dates.

@@

Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical toolkit, are useful for summarizing overall deviations across days and households. Figure \ref{fig:h12} and \ref{fig:h34} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing through Figure \ref{fig:h12}, their week day energy use distinguishes from their weekends. We can exactly tell when their air conditioner and heater are turned on. Heating keeps functioning in consecutive hours at household 2, which is evident in the mid July; while household 1 uses them cautiously. This finding helps explain the strips and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous figures. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h34} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.

```{r h12, fig.height = 10, fig.cap = "Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June."}
```

```{r h34, fig.height = 10, fig.cap = "Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating."}
```

# Discussion
\label{sec:discussion}

@@

>>>>

As a data restructuring tool, the interactivity of calendar-based display can be easily enabled, as long as the interactive graphic system remains true to the spirit of the grammar of graphics, for example **plotly** [@plotly] in R. As a standalone display, an interactive tooltip can be added to show labels when mousing over it in the calendar layout, for example the hourly count with the time of day. It is difficult to sense the values from the static display, but the tooltip makes it possible. Options in function `frame_calendar` can be ported to a form of selection button or text input in a graphical user interface like shiny \ref{XXX}. The display will update on the fly accordingly via clicking or text input, as desired.

Linking calendar displays to other types of charts is valuable to visually explore the relationships between variables. An example can be found in \ref{YYY}. The calendar most naturally serves as a tool for date selection: by selecting and brushing the glyphs in the calendar, it subsequently highlights the elements of corresponding dates in other time-based plots. Conversely, selecting on weather data plots, linked to the calendar can help to assess if very hot/cold days and heavy rain affect the number of people walking in downtown Melbourne. The linking between weather data and calendar display is achieved using the common dates.

@@

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display the data in calendar layout individually for each household, unfolding their day-to-day life. Glancing over household 1, you can see that their overall energy use is low. Their week day energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months in the evening and weekends. In household 2, heating keeps functioning for consecutive hours, which is evident in the mid July; while household 1 uses heating cautiously. These observations help to explain the stripes and clusters in Figure \ref{fig:hod}. The calendar plots speak the stories about vacation time that are untold by previous plots. Household 1 is on vacation over three weeks of June, and household 2 was also away for holidays during Christmas and the second week of June. Figure \ref{fig:h3} shows household 3 takes two one-month-long family trips in September till early October and in June/July, and household 4 is away over two or three weeks in early October, December and late June. The use of air conditioning and heating leaves no trace in these two households.
# Discussion
\label{sec:discussion}

@@

```{r h1, fig.height = 5, fig.cap = "Calendar display for household 1, indicates higher weekend usage, and in the summer months, November-February. It seems that they took a vacation in June."}
```

```{r h2, fig.height = 5, fig.cap = "Calendar display for household 2, reveals their tendency to use air conditioning and heating continuously. Not many vacation were taken."}
```

```{r h3, fig.height = 5, fig.cap = "Calendar display for household 3. Their energy use reveals higher energy use in the winter months, with multiple peaks daily on both week days and weekends. There are some high peaks in summer, perhaps indicating occasional air conditioner use. There have been several long vacations in the past year."}
```

```{r h4, fig.height = 5, fig.cap = "Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, and June."}
```

### 2018-10-22 main.tex
di finished

As a data restructuring tool, the interactivity of calendar-based
display can be easily enabled, as long as the interactive graphic system
remains true to the spirit of the grammar of graphics, for example
\textbf{plotly} \citep{plotly} in R. As a standalone display,
interactive tooltip can be added to show the actual values of a data
point when mousing over it in the calendar layout, for example the
hourly count with the time of day. It is difficult to sense the values
in static display, but the tooltip makes it possible. Options in
function \texttt{frame\_calendar} can be ported to a form of selection
buttons or text input. The display will update on the fly accordingly
via clicking or inputing, as desired.

Linking calendar displays to other types of charts is of great value to
visually explore the interactions with many factors. It most naturally
serves as a toolbox of date selection. By selecting and brushing the
glyphs in the calendar, it subsequently highlights the elements of
corresponding dates in other time-based plots, or vice versa. For
example, it would be interesting to learn if very hot/cold days and
heavy rain affect the number of people walking in downtown Melbourne,
especially outdoor areas. Melbourne's daily temperatures and
precipitations can be acquired, and plotted against the dates. The
linking between weather data and calendar display is achieved using the
common dates.

@@

Figures \ref{fig:dow} and \ref{fig:hod}, part of a traditional graphical
toolkit, are useful for summarizing overall deviations across days and
households. Figure \ref{fig:h12} and \ref{fig:h34} display the data in
calendar layout individually for each household, unfolding their
day-to-day life. Glancing through Figure \ref{fig:h12}, their week day
energy use distinguishes from their weekends. We can exactly tell when
their air conditioner and heater are turned on. Heating keeps
functioning in consecutive hours at household 2, which is evident in the
mid July; while household 1 uses them cautiously. This finding helps
explain the strips and clusters in Figure \ref{fig:hod}. The calendar
plots speak the stories about vacation time that are untold by previous
figures. Household 1 is on vacation over three weeks of June, and
household 2 was also away for holidays during Christmas and the second
week of June. Figure \ref{fig:h34} shows household 3 takes two
one-month-long family trips in September till early October and in
June/July, and household 4 is away over two or three weeks in early
October, December and late June. The use of air conditioning and heating
leaves no trace in these two households.

{\centering \includegraphics[width=\textwidth]{figure/h12-1}

\caption{Calendar displays for household 1 and 2. It reveals their regular tendency of using air conditioning and heating and vacation time periods. For example, household 2 leaves heating on consecutively in the mid July, is on holiday for Christmas and the second week of June.}\label{fig:h12}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h34-1}

\caption{Calendar displays for household 3 and 4. Household 3 are on long trips twice in the past year, while household 4 takes three short trips in October, December, and June. Both households leave no clue if they use air conditioning and heating.}\label{fig:h34}
\end{figure}

\section{Discussion}\label{discussion}

\label{sec:discussion}

@@

>>>>

As a data restructuring tool, the interactivity of calendar-based
display can be easily enabled, as long as the interactive graphic system
remains true to the spirit of the grammar of graphics, for example
\textbf{plotly} \citep{plotly} in R. As a standalone display, an
interactive tooltip can be added to show labels when mousing over it in
the calendar layout, for example the hourly count with the time of day.
It is difficult to sense the values from the static display, but the
tooltip makes it possible. Options in function \texttt{frame\_calendar}
can be ported to a form of selection button or text input in a graphical
user interface like shiny \ref{XXX}. The display will update on the fly
accordingly via clicking or text input, as desired.

Linking calendar displays to other types of charts is valuable to
visually explore the relationships between variables. An example can be
found in \ref{YYY}. The calendar most naturally serves as a tool for
date selection: by selecting and brushing the glyphs in the calendar, it
subsequently highlights the elements of corresponding dates in other
time-based plots. Conversely, selecting on weather data plots, linked to
te calendar can help to assess if very hot/cold days and heavy rain
affect the number of people walking in downtown Melbourne. The linking
between weather data and calendar display is achieved using the common
dates.

@@

Figure \ref{fig:h1}, \ref{fig:h2}, \ref{fig:h3} and \ref{fig:h4} display
the data in calendar layout individually for each household, unfolding
their day-to-day life. Glancing over household 1, you can see that their
overall energy use is low. Their week day energy use is distinguishable
from their weekends, indicating a working household. The air conditioner
appears to be used in the summer months in the evening and weekends. In
household 2, heating keeps functioning for consecutive hours, which is
evident in the mid July; while household 1 uses heating cautiously.
These observations help to explain the stripes and clusters in Figure
\ref{fig:hod}. The calendar plots speak the stories about vacation time
that are untold by previous plots. Household 1 is on vacation over three
weeks of June, and household 2 was also away for holidays during
Christmas and the second week of June. Figure \ref{fig:h3} shows
household 3 takes two one-month-long family trips in September till
early October and in June/July, and household 4 is away over two or
three weeks in early October, December and late June. The use of air
conditioning and heating leaves no trace in these two households. \#
Discussion \label{sec:discussion}

@@

{\centering \includegraphics[width=\textwidth]{figure/h1-1}

\caption{Calendar display for household 1, indicates higher weekend usage, and in the summer months, November-February. It seems that they took a vacation in June.}\label{fig:h1}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h2-1}

\caption{Calendar display for household 2, reveals their tendency to use air conditioning and heating continuously. Not many vacation were taken.}\label{fig:h2}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h3-1}

\caption{Calendar display for household 3. Their energy use reveals higher energy use in the winter months, with multiple peaks daily on both week days and weekends. There are some high peaks in summer, perhaps indicating occasional air conditioner use. There have been several long vacations in the past year.}\label{fig:h3}
\end{figure}

{\centering \includegraphics[width=\textwidth]{figure/h4-1}

\caption{Calendar display for household 4, shows energy use mostly in the evenings and on weekends. Three short trips were taken in October, December, and June.}\label{fig:h4}
\end{figure}
